---
title: "Graphs using R"
description: |
  Here is an example of my graphing skills using R for a class assignment.
author:
  - name: Madeleine Deisen
date: 04-18-2021
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(plotly)
library(nycflights13)
```

I used the Flights dataset and Plotly in R to create a bar chart showing the breakdown of flights by airline that originate from JFK airport and are more than 400 minutes in length.

```{r}
question7_flights <- filter(flights, origin=="JFK" & air_time>400) %>%
    count(carrier)

fig <- plot_ly(
  x = question7_flights$carrier,
  y = question7_flights$n,
  name = "Flights from JFK Airport Longer Than 400 Minutes",
  type = "bar"
)

fig
```

I also created a donut chart showing the share of flights each airline has of flights with a destination of Daniel K. Inouye International Airport (HNL) in Honolulu.

```{r}
flights_data <- filter(flights, dest=="HNL") %>%
  count(carrier)
flights_data

fig <- plot_ly(labels = flights_data$carrier, values = flights_data$n) %>%
  add_pie(hole = 0.6)
fig
```

Finally, I created a scatterplot chart for flights with a destination of Daniel K. Inouye International Airport (HNL) in Honolulu that shows the relationship between the departure delay and arrival delay.

```{r}
flights_HNL <- filter(flights, dest=="HNL")
flights_HNL

fig <- plot_ly(data = flights_HNL, x = flights_HNL$dep_delay, y = flights_HNL$arr_delay)
fig 

```
